On the marginal value of swimming in woodland caribou

### 2021-05-25 paper/manuscript.Rmd
P5

Swimming behavior was common among GPS radio-collared caribou in the population (n = 29, for collaring
details see Peignier et al. 2019). We identified `r nevents` swimming events over three years (Figure
2). In total, 13 of 29 collared female caribou swam among islands (Figure 2). Of the caribou that
swam, caribou swam on average approximately `r neventidMedian` (range = `r neventidMin`-` neventidMax`) times per year and remained on each island for a median of `r dur` (range = 
`r durMin`-`r durMax`) days before swimming again. We found that caribou residency increased
proportionally with the size of the island, such that caribou spent less time on smaller islands and
more time on larger islands, providing preliminary evidence for links between forage limitation and
the marginal value theorem (Figure 2B).

>>>>

Swimming behavior was common among GPS radio-collared caribou in the population (n = 29, for collaring details see Peignier et al. 2019). We identified `r nevents` swimming events over three years (Figure 2). In total, 13 of 29 collared female caribou swam among islands (Figure 2). Of the caribou that swam, caribou swam on average approximately `r neventidMedian` (range = `r neventidMin`-` neventidMax`) times per year and remained on each island for a median of `r dur` (range =  `r durMin`-`r durMax`) days before swimming again. We found that caribou residency increased proportionally with the size of the island for islands larger than approximately 0.1 km^2, such that caribou spent less time on smaller islands and more time on larger islands, providing preliminary evidence for links between forage limitation and the marginal value theorem (Figure 2B). In many cases, the smaller islands in the archipelago are forage limited and the larger islands provide greater opportunities to forage.
